Perceptual Symbol Grounding in \\Holographic Memories

### 2016-12-18 papers/hrr-paper/paper.tex
Added Coordinate Encoding subsection

	\subsection{Encoding scalar symbol as radial basis functions}

@@

>>>>

	\subsection{Encoding scalar symbols}

@@

	\subsection{Encoding coordinate symbols}

		Encoding coordinate symbols works in a manner very similar to encoding scalar symbols. Depending on the number of coordinates the symbolic vectors shape is reinterpreted. 2D coordinates, for instance, require a matrix. This matrix represents the entire coordinate space and on it 2D Gaussian distributions are sampled. It can be viewed as a heat map, as displayed in figure \ref{fig:encoding-coord}.	The matrix will still be treated as a vector when it comes to running operations on it and must also be permuted. Since the value space now has more dimensions the size of the vector has to be raised accordingly to achieve performance similar to that of scalar symbol encoding.

		An attempt has been made to overcome the curse of dimensionality by splitting the vector up in the number of dimensions and simply encoding the value for each dimension in the resulting sub-vectors. Unfortunately it then becomes impossible to differentiate among multiple coordinates encoded in the same vector. Specifically, when decoding, there is no way to know which of the values in separate sub-vectors belong to each other and which don't. On the other hand if only a single coordinate needs to be bound to another symbol this approach is still feasible and will permit the use of smaller vectors for high accuracy. Concretely, for $d$ dimensions, splitting up the vector will require the size to be raised by a factor of $d$ to maintain the same accuracy. Reinterpreting the shape will require the size to increase exponentially by the power of $d$ to keep the accuracy.
